\postepi{

\emph{Ergo aegre rastris terram rimantur et ipsis}\\
\emph{unguibus infodiunt fruges montisque per altos}\\
\emph{contenta cervice trahunt stridentia plaustra.}\\
\emph{Non lupus insidias explorat ovilia circum}\\
\emph{nec gregibus nocturnus obambulat; acrior illum}\\
\emph{cura domat; timidi dammae cervique fugaces}\\
\emph{nunc interque canes et circum tecta vagantur.}\\
\emph{Iam maris immensi prolem et genus omne natantum}\\
\emph{litore in extremo, ceu naufraga corpora, fluctus}\\
\emph{proluit; insolitae fugiunt in flumina phocae.}\\
\emph{Interit et curvis frustra defensa latebris}\\
\emph{vipera et attoniti squamis adstantibus hydri.}\\
\emph{Ipsis est aër avibus non aequus et illae}\\
\emph{praecipites alta vitam sub nube relinquunt.}\\
\emph{Praeterea iam nec mutari pabula refert}\\
\emph{artes nocent quaesitaeque; cessere magistri}\\
\emph{Phillyrides Chiron Amythaoniusque Melampus.}\\
\emph{Saevit et in lucem Stygiis emissa tenebris}\\
\emph{pallida Tisiphone Morbos agit ante Metumque,}\\
\emph{inque dies avidum surgens caput altius effert:}\\
\emph{Balatu pecorum et crebris mugitibus amnes}\\
\emph{arentesque sonant ripae collesque supini:}\\
\emph{Iamque catervatim dat stragem atque aggerat ipsis}\\
\emph{in stabulis turpi dilapsa cadavera tabo}\\
\emph{donec humo tegere ac foveis abscondere discunt.}\\
\emph{Nam neque erat coriis usus nec viscera quisquam}\\
\emph{aut undis abolere potest aut vincere flamma;}\\
\emph{ne tondere quidem morbo inluvieque peresa}\\
\emph{vellera nec telas possunt attingere putris;}\\
\emph{verum etiam invisos si quis temptarat amictus,}\\
\emph{ardentes papulae atque immundus olentia sudor}\\
\emph{membra sequebatur nec longo deinde moranti}\\
\emph{tempore contactos artus sacer ignis edebat.}\\

\qsource{Virgil}

}

\postepi{

\emph{Then, they say, for the sole time in these parts,}\\
\emph{White cows could not be found for Juno's rites,}\\
\emph{And buffaloes, instead, in ill-matched pairs,}\\
\emph{Drew chariots to the lofty treasure-house.}\\
\emph{Men hacked the ground with rakes, and dug a seed}\\
\emph{With blistered fingers, hitched themselves to carts}\\
\emph{And, straining forward, dragged the creaking loads.}\\
\emph{Wolves ceased to prowl at night around the fold,}\\
\emph{For sharper worries preyed upon their minds;}\\
\emph{The timid roe and flying stag made friends}\\
\emph{With hounds and wandered all around the farms.}\\
\emph{The brood of the mighty sea was washed ashore}\\
\emph{Like flotsam from a shipwreck, and the seals}\\
\emph{Escaped to unfamiliar inland streams.}\\
\emph{The viper died defenseless in her lair}\\
\emph{And water snakes, their scales erect in fear.}\\
\emph{Birds found the air too heavy for their wings}\\
\emph{And, plunging earthward, left their lives aloft.}\\
\emph{Change of pasture made no difference}\\
\emph{And remedies effected only harm;}\\
\emph{The masters of the healing arts gave up.}\\
\emph{Pale Fury, flown from Hell's depths to the light,}\\
\emph{Tisiphone, drove on Disease and Fear,}\\
\emph{Her greedy head rose higher every day.}\\
\emph{The bleating of the herds, their steady moans,}\\
\emph{Filled all the river beds and thirsty banks,}\\
\emph{Reverberating through the supine hills.}\\
\emph{The Fury dealt out multitudinous deaths,}\\
\emph{Heaving up cadavers in the stalls,}\\
\emph{Rotting corpses stank and putrefied,}\\
\emph{Until at last men buried them in pits.}\\
\emph{The hides were useless, and the flesh so foul}\\
\emph{That fire and water could not salvage it;}\\
\emph{None could shear the fleece, nor touch the web.}\\
\emph{If someone tried to wear the loathsome cloth,}\\
\emph{He burned and blistered, rank repulsive sweat}\\
\emph{Poured off his fetid limbs; and, soon enough,}\\
\emph{His stricken body felt the sacred fire.}\\

\qsource{Virgil}

}
