\hypertarget{glossary}{%
\chapter{Glossary}\label{glossary}}

\begin{description}
\tightlist
\item[Ackle]
The mountain home of much of the goblin nation in Britain.
\item[Agenspræc]
Literally ``other-speech,'' this term of art refers to the incantation
required to authorize or remove a Floo connection to an established
network.
\item[Alþing]
The fortress-like headquarters of the Council of Westphalia, the Alþing
(or ``All-\textbf{Thing}'') serves as an information warehouse and the
site of fiery debates.
\item[Americas]
See \textbf{Westphalia, Council of}.
\item[Bogdanova, Agapa ``Ilya'' Ilyinichna]
Head of the Office for the Detection and Confiscation of Counterfeit
Defensive Spells and Protective Objects, Ilya is an efficient older
witch of Russian extraction. She is a graduate of the Durmstrang
Institute, and maintains close ties with its faculty.
\item[Bones, Amelia]
As the Chief Warlock, Madame Amelia Bones serves as the leader of the
\textbf{Wizengamot} and administrator of the justice system of Magical
Britain. As Supreme Mugwump, she leads the \textbf{International
Confederation of Wizards}.
\item[Cappadocia]
Magical Cappadocia, also called the Exarchate of Cappadocia, is a
magical state that controls much of the Balkans and Turkey. It is ruled
by an elite class known as the \emph{sakellarioi} (in continuity with
the Byzantine state from which it descended), although nominally headed
by a single powerful \emph{Strategos}. They are relatively poor when
compared with the rest of the world, and the two dominant languages are
Greek and Turkish. They have belligerent relations with \textbf{Cyprus}.
\item[Caucasus]
Magical Caucasus is officially a single magical state north of
\textbf{Cappadocia}, but in practice is a fractious conglomeration of
small regions with little to unite them but convenience. Delegate status
to the \textbf{International Confederation} is frequently doled out as a
sop to potential rivals of local strongmen, and in practice the Caucasus
tends to lean heavily in favor towards Russia and the European
contingent.
\item[Charlevoix, Odette]
A member of the \textbf{Returned }of \textbf{Hermione Granger},
Charlevoix is of French extraction. She is quiet and shy by nature,
which combines oddly with the extremism of the Returned. She looks just
like your aunt.
\item[Covenant, Tilly]
Assistant Head of the Office for the Detection and Confiscation of
Counterfeit Defensive Spells and Protective Objects.
\item[Curd]
A small community of goblins in Ireland.
\item[Cyprus]
Magical Cyprus is a small and wealthy state in the Mediterranean with
strong historical ties to Britain. They have had fractious relations
with \textbf{Cappadocia}.
\item[Diggory, Cedric]
Head of the Department of Magical Law Enforcement and widely considered
to be a prodigy, having risen to his position with remarkable speed.
\item[Eleusinian Mysteries]
The magical cabal that ruled Ancient Rome during much of its early
history. After their fall and some discord, they were succeeded by the
Caesars and Muggle rule.
\item[Euphoric]
An addict of Euphoria Elixir, unable to resist compulsively indulging in
that potion's rush of pleasure and delight.
\item[Floo Flounder]
An American device, these take the form of small bellows on the floor
and dispense a set amount of Floo powder. It is slightly safer and
considerably cleaner than using manual pinches of the stuff, especially
for children and the elderly.
\item[Franklin's Nez]
A popular Boston tavern, conspicuous for having Pensieves and a variety
of exhilarating or pleasurable memories to rent.
\item[Free States]
Several different small states in the south of Africa that tend to agree
on matters of international politics but which endure frequent friction
among themselves: the Orange Free State, the Zulu Free State, and the
Transvaal Free State. The Free States are also notable for being one of
the areas where the magical world is wholly out of sync with the Muggle
world's borders.
\item[Goddess, The]
See \textbf{Granger, Hermione Jean}.
\item[Göreme]
A prison complex of the Exarchate of \textbf{Cappadocia}, where
Dementors are housed. They are kept a maximum distance away from
prisoners, who are there to provide sustenance, not suffer punishment.
\item[Granger, Hermione Jean]
Also melodramatically known as the ``Goddess,'' Hermione is an
international envoy for the \textbf{Treaty for Health and Life} and an
activist for various causes (most prominently the abolition of
Dementors).
\item[Grindelwald, Gellert]
A Hungarian wizard who was educated at the Durmstrang Institute and who
rose to power as a Dark Lord with the stated intention of overturning
the Statute of Secrecy and improving the lives of Muggles everywhere
under a benevolent dictatorship, modeled after Plato's \emph{The
Republic}.
\item[Hig, Councilor Regulus ``Reg'' Black-Horse]
Arguably the most influential Councilor on the \textbf{Council of
Westphalia}, Hig has risen to power despite his years spent fighting for
the rights of Muggles and Beings. His closest ally is Councilor
\textbf{Limpel Tineagar}.
\item[Hírnökei]
The ``Vég Hírnökei,'' or ``Heralds of the End,'' were the fighting force
assembled by \textbf{Gellert Grindelwald} and indoctrinated with a
strange kind of fanaticism. They mostly came from former Durmstrang
Institute students and the ranks of local warlords from Eastern Europe,
and used Hungarian as a lingua franca.
\item[Howard Prison]
A purpose-built prison for magical Britain, created to replace Azkaban
after its destruction at the end of 1992.
\item[International Confederation of Wizards]
The international assembly of wizardkind. It is governed by majority
vote, and delegates are apportioned to states based on magical
population. It is similar to the Muggle United Nations, with the
differences of meeting infrequently, having no permanent headquarters,
and occasionally being efficacious.
\item[International Statute for Health and Life]
An attempt at an international law setting into place requirements for
all nations to have their sick and elderly restored to health at the
\textbf{Tower. }It failed to pass in the \textbf{International
Confederation of Wizards}, and was one of Harry Potter's early failures.
See also \textbf{Treaty for Health and Life.}
\item[Lectenberg, Susie]
A member of the \textbf{Returned} of \textbf{Hermione Granger}, Susie
was a longtime petty criminal who once ran a business selling
unauthorized portkeys and fraudulent potions out of Diagon Alley. She
was given an unusually harsh sentence of two years in Azkaban. Susie is
quite talkative in the pseudo-Dickensian manner of many of the residents
of Diagon.
\item[Li, Hyori]
A member of the \textbf{Returned} of \textbf{Hermione Granger}, Hyori
was a high-ranking duelist on the British circuit before she was
imprisoned in Azkaban. She is extremely laconic, but still waters run
deep.
\item[\emph{Mercantile, The}]
The leading newspaper of magical Boston. It is noted for having an
excellent reporting staff with top-notch investigations accompanied by
entirely deluded editorials.
\item[Minister for Magic]
Purportedly the leader of the government of magical Britain, although
the Minister for Magic has historically been secondary to whomever has
the greatest support in the Wizengamot, thanks to a governmental
structure that strongly favors the legislative branch over the executive
one. Recent Ministers in chronological order have been: Millicent
Bagnold, Bartemius Crouch, Cornelius Fudge, Rufus Scrimgeour, Pius
Thicknesse, Junius Simplewort Smith, and Carmel N'goma (the current
Minister).
\item[Moody, Alastor ``Mad Eye'']
He's probably watching you now.
\item[Mukwooru]
A powerful Comanche medicine man in antiquity, who probably lived during
the fifteenth or sixteenth century.
\item[N'goma, Carmel]
See \textbf{Minister for Magic.}
\item[Nutcombe Society, The]
The only currently extant organization for hags in Britain; it has only
a handful of members, but it is an important support group for those
hags who wish to live an alternative lifestyle.
\item[Pirrip, Phillip ``Pip'']
A relatively new auror assigned to the \textbf{Tower}, given an
unfortunate name by his father, a Muggle literature professor.
\item[Potter-Evans-Verres, Harry James]
Also known as ``Harry Potter'' or the ``\textbf{Tower},'' Harry lives in
a box, heals people, and schemes.
\item[Price, Esther]
A member of the \textbf{Returned} of \textbf{Hermione Granger}, Esther
is an American by nationality, and her imprisonment in Azkaban (for
illegally breeding and selling sphinxes) had been a matter of great
contention between the magical States and magical Britain.
\item[Rejuvenation]
The official name for the treatment to restore youth at the
\textbf{Tower}. The process is done by any of the available healers and
certified in every case by Harry Potter himself. Most typically,
applicants are restored to the best approximation of their youthful self
(usually at the rough physiological age of 25). There is a tendency for
distinctive features to be lost or altered during the process, although
this can be minimized if the applicant brings sufficient pictures of
themselves when young.
\item[Returned, The]
A small group of witches and wizards who work under the direction of
\textbf{Hermione Granger}. They have several aims, but their paramount
purposes are the elimination of Dementors and the end of suffering in
the world. They do not lack ambition. Also see \textbf{Charlevoix,
Odette; Lectenberg, Susie; Li, Hyori; Price, Esther; Smith, Simon;
Tonks, Nymphadora; or Urg of the Returned.}
\item[Room 101]
Everyone knows what's in Room 101. The thing that is in Room 101 is the
worst thing in the world.
\item[Russell Center, The]
One of the two major schools of magic in North America, the Russell
Center focuses on practical application and specialization. Students
choose a specific course of study in addition to their general
education, and are required to master their chosen field.
\item[Safety Pole]
See \textbf{Tower, The}.
\item[Safety Stick]
See \textbf{Tower, The}.
\item[Salor Sprig, The]
The Salor Sprig is a revered silver birch sapling at the centre of a
sacred clearing in the Forbidden Forest near Hogwarts, in the northwest
of their designated lands. The Sprig remains the same, year after year,
never maturing from its sapling stage. According to legend, this is
because it accords the centaurs too much respect to obstruct them in
their studies or their frolics. A small group of buildings has been
built among the trees near the Sprig, and form a rough center to their
community.
\item[Satomi's Dogs]
A powerful set of magical items once employed by \textbf{Gellert
Grindelwald}, these crystal devices granted that Dark Lord some unknown
power to sustain himself. The secret of their means and method was
restricted to only a handful of people.
\item[Sawad]
The group of magical states in the Middle East, a relic of ancient
magical despots that are still customarily considered a unit, despite
their actual independence and occasionally divergent interests.
\item[Science Program]
A four-year educational track at Hogwarts School of Witchcraft and
Wizardry, the Science Program features two years of general magical
studies and two years of scientific training. It was introduced in the
1992-1993 school year as an optional vocational program.
\item[Shacklebolt, Kingsley]
Former Head of the Department of Magical Law Enforcement, succeeding
\textbf{Amelia Bones} upon her ascension to Chief Warlock and dismissed
several years later.
\item[Shichinin]
A wildly effective and wildly unconventional trio of Hit Wizards.
\item[Smith, Junius Simplewort]
See \textbf{Minister for Magic.}
\item[Smith, Simon]
A member of the \textbf{Returned }of \textbf{Hermione Granger}, Simon is
Scottish and proud of it. He once had a drinking problem and a fighting
problem, and in time it led to Azkaban.
\item[Sontag]
A hamlet of medieval Magical Britain, located in the West Country. It
was abandoned in the fourteen century. It was near Godric's Hollow, the
magical community from which Sontag once sprang due to disagreements
over the prohibition of werewolves.
\item[Ten Thousand, The]
Colloquial term used to refer to those twelve magical Asian states with
a common Taoist and Confucian heritage.
\item[Tidewater]
The main magical community of Boston, Tidewater is a quaint and narrow
dockside village set within Boston. It is dominated, metaphorically and
literally, by the stately \textbf{Alþing.}
\item[Tineagar, Councilor Limpel]
A veteran of the \textbf{Council of Westphalia} and the ally of
\textbf{Reg Hig}, Tineagar is generally disagreeable. She is an expert
in Floo networks and similar magics.
\item[Thing]
In addition to being a generic noun, it also historically refers to
governing assemblies in many Germanic countries. It is still used in
some areas as a term for any magical assembly of lawmakers.
\item[Tonks, Nymphadora]
A member of the \textbf{Returned }of \textbf{Hermione Granger}, Tonks is
a metamorphmagus and kind of a pain in the ass.
\item[Treaty for Health and Life]
A formal agreement between different magical states, sponsored by
Britain and guided by the \textbf{Tower}, that directs the establishment
of Safety Poles in magical communities, the free availability of Safety
Sticks and elite Healer's Kits, and a variety of other social and
economic changes.
\item[Tower, The]
The clinic and sprawling research center on the grounds of Hogwarts, led
by \textbf{Harry Potter} and dedicated to the perfect healing of any
wound or sickness, free of charge. Travel to the Tower is free and
instantaneous with Safety Sticks or a Safety Pole. Not technically a
part of the government of magical Britain. Also see \textbf{Tower School
of Doubt.}
\item[Tower School of Doubt, The]
The institute of higher learning established by \textbf{Harry Potter}
and designed to systematically apply the principles of the scientific
method to the study of magic. Works closely with the Unspeakables of the
Department of Mysteries in the government of magical Britain.
\item[\emph{Unbreakable Honour}]
The underground newspaper published by Draco and Narcissa Malfoy. It has
a worldwide circulation, and has made them the leaders of the minority
campaign against the current leadership of Britain and the
\textbf{Treaty for Health and Life}.
\item[Urg the Unclean]
The charismatic and brilliant leader of the fifth goblin rebellion of
1720-1722 C.E., the ``Great Rebellion.''
\item[Urg the Returned]
A member of the \textbf{Returned }of \textbf{Hermione Granger}, Urg was
imprisoned in Azkaban as a gesture of dominance by the
\textbf{Wizengamot}, asserting their authority over the goblins. He was
one of the first goblins to legitimately purchase a masterwork wand in
many centuries.
\item[Vanishing Room]
A natural extension of the concept of the Vanishing Cabinet, constructed
for easy international shipping. Put things in, close the door, and
they're teleported to the twin room somewhere else in the world.
\item[Veres Kezek]
The ``Red Hands,'' one of the death squads of \textbf{Gellert
Grindelwald} during his reign of terror. See also \textbf{Hírnökei.}
\item[Walpurgisnacht]
``Walpurgis Night,'' the night of April 30th, is a night of celebration
for many Muggles. It is named after St.~Walpurga, and in many countries
in Europe is marked by the building of big bonfires, evoking the fires
in which witches were once burned. It is a grim night of remembrance for
wizardkind.
\item[Weasley, Percy]
Senior Undersecretary Percy Weasley is the effective head of government
of Magical Britain, serving under a rotating and mostly meaningless
series of Ministers. He is seen as slightly priggish by his underlings,
but his efficiency and concern for detail are peerless.
\item[Westphalia, Council of]
The Mystical and Benevolent Council of Westphalia, also called the
\textbf{Westphalian Council} and headquartered in the \textbf{Alþing},
is the most powerful magical organization in the United States of
America and Canada. For years, it has acted as the self-appointed
guardian of the interests of both North and South America (or at least,
those interests as it sees them). It has controlled a large majority of
the Magical Congress of the United States for many years, making it the
effective ruler of the country and arbiter of its delegates to the
\textbf{International} \textbf{Confederation of Wizards}.
\item[Westphalia, Peace of]
A formative historical event in both the Muggle and magical worlds, the
Peace ended multiple wars and established norms regarding the formal
existence of states and their rights under international law. Soon led
to the founding of the \textbf{International Confederation of Wizards.}
\item[Wizengamot]
The supreme judicial and legislative body of magical Britain, the
Wizengamot is led by \textbf{Amelia Bones} and populated overwhelmingly
with supporters of \textbf{Harry Potter} and his initiatives. It is
composed predominantly of the representatives of Noble Houses, as well
as elected Tribunes from other constituent bodies.
\item[Záh Kardja]
The ``Sword of Záh,'' one of the death squads of \textbf{Gellert
Grindelwald} during his reign of terror. Named in honor of the Hungarian
Felician Záh. See also \textbf{Hírnökei}.
\end{description}
