\postepi{

\foreignlanguage{greek}{\textgreek{\emph{Πρὶν μὲν γὰρ ζώεσκον ἐπὶ χθονὶ
φῦλ᾽ ἀνθρώπων}}}\\
\foreignlanguage{greek}{\textgreek{\emph{νόσφιν ἄτερ τε κακῶν καὶ ἄτερ
χαλεποῖο πόνοιο}}}\\
\foreignlanguage{greek}{\textgreek{\emph{νούσων τ᾽ ἀργαλέων, αἵ τ᾽
ἀνδράσι Κῆρας ἔδωκαν.}}}\\
\foreignlanguage{greek}{\textgreek{\emph{αἶψα γὰρ ἐν κακότητι βροτοὶ
καταγηράσκουσιν.}}}\\
\foreignlanguage{greek}{\textgreek{\emph{ἀλλὰ γυνὴ χείρεσσι πίθου μέγα
πῶμ᾽ ἀφελοῦσα}}}\\
\foreignlanguage{greek}{\textgreek{\emph{ἐσκέδασ᾽: ἀνθρώποισι δ᾽ ἐμήσατο
κήδεα λυγρά.}}}\\
\foreignlanguage{greek}{\textgreek{\emph{μούνη δ᾽ αὐτόθι Ἐλπὶς ἐν
ἀρρήκτοισι δόμοισιν}}}\\
\foreignlanguage{greek}{\textgreek{\emph{ἔνδον ἔμιμνε πίθου ὑπὸ
χείλεσιν, οὐδὲ θύραζε}}}\\
\foreignlanguage{greek}{\textgreek{\emph{ἐξέπτη: πρόσθεν γὰρ ἐπέλλαβε
πῶμα πίθοιο}}}\\
\foreignlanguage{greek}{\textgreek{\emph{αἰγιόχου βουλῇσι Διὸς
νεφεληγερέταο.}}}\\
\foreignlanguage{greek}{\textgreek{\emph{ἄλλα δὲ μυρία λυγρὰ κατ᾽
ἀνθρώπους ἀλάληται:}}}\\
\foreignlanguage{greek}{\textgreek{\emph{πλείη μὲν γὰρ γαῖα κακῶν, πλείη
δὲ θάλασσα:}}}\\
\foreignlanguage{greek}{\textgreek{\emph{νοῦσοι δ᾽ ἀνθρώποισιν ἐφ᾽
ἡμέρῃ, αἳ δ᾽ ἐπὶ νυκτὶ}}}\\
\foreignlanguage{greek}{\textgreek{\emph{αὐτόματοι φοιτῶσι κακὰ θνητοῖσι
φέρουσαι}}}\\
\foreignlanguage{greek}{\textgreek{\emph{σιγῇ, ἐπεὶ φωνὴν ἐξείλετο
μητίετα Ζεύς.}}}\\
\foreignlanguage{greek}{\textgreek{\emph{οὕτως οὔτι πη ἔστι Διὸς νόον
ἐξαλέασθαι.}}}\\}

\postepi{
\emph{At first the tribes of men had lived upon the earth}\\
\emph{apart and free of evils and of tiresome toil}\\
\emph{and hard diseases, which have brought to men their dooms,}\\
\emph{because by hardship mortal men are quickly aged.}\\
\emph{But with her hands the woman raised the jar's great lid,}\\
\emph{released all these, devising grievous cares for men.}\\
\emph{Alone there, Hope, in her indestructible home,}\\
\emph{remained within, beneath the lip, nor by the door}\\
\emph{escaped, because the vessel's lid had stopped her first,}\\
\emph{by will of aegis-bearing, cloud-compelling Zeus.}\\
\emph{Among the people wander countless miseries;}\\
\emph{the earth is full of evils, and the sea is full;}\\
\emph{diseases come by day to people, and by night,}\\
\emph{spontaneous, rushing, bringing mortals evil things}\\
\emph{in silence, since contriving Zeus removed their voice.}\\
\emph{And thus from Zeus's mind there can be no escape.}\\
\qsource{Hesiod, ``Works and Days''}

}
